Untitled

### 2017-09-05 PaperCode.Rmd
Cascading
Addede code to being trying to cascade. Included two new functions to smooth the code. the first identifies validnodes for the injection vector. the second balances the generation and demand of the valid nodes across islolated graph componants

@@

@@

```{r}
PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

@@

#Merton

MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

@@

Rural Urban split
```{r}
setwd(DataFolder)

Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
  setNames(make.names(names(.))) %>%
  rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
  select(LAD11CD, PercRural) %>%
  mutate(PercRural = as.numeric(PercRural))

#Update Gateshead and Northumberland Codes
Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"

Combine1ExO <- Combine1ExO %>%
  left_join(Rural, by = "LAD11CD")

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
  left_join(Rural, by = "LAD11CD") %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

@@

ModelStats %>% ggplot(., aes(x= Accuracy)) +geom_density()

ModelStats %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

ModelStats %>% ggplot(., aes(x= AccuracyPValue)) +geom_density()
ModelStats %>% ggplot(., aes(x= Kappa)) +geom_density()

t.test(ModelStats$Accuracy, ModelStats$AccuracyNull, alternative = "greater")

test <- ModelStats %>% 
  select( X.Intercept., LUPdepExt, maxPerc, pricepercent) %>%
  gather

@@

Outcome <- bind_rows(data_frame(model = "generic", Accuracy = ModelStats2$Accuracy), 
data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )

Outcome %>%
  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3)

@@

@@

#Linear
set.seed(1983)
MultiCheckL <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

      Comp.Type = case_when(
      .$Significant.Competition<0.5-tol ~"No",
      .$Significant.Competition>0.5 + tol ~"Yes",
      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
      )
  ) %>%
  select(-Reference)

@@

>>>>

98nmol/L

@@

BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
 left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
  StructureData()

@@

```{r}
BournemouthDATA <- read_excel("BournemouthDiscountsLSOA_R.xlsx" )[1:4] %>%
  StructureData(c(6,8,9:13))

PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
  StructureData(lowuse = c(5,11:14,18))

@@

@@

Rural Urban split
```{r}
# setwd(DataFolder)
# 
# Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
#   setNames(make.names(names(.))) %>%
#   rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
#   select(LAD11CD, PercRural) %>%
#   mutate(PercRural = as.numeric(PercRural))
# 
# #Update Gateshead and Northumberland Codes
# Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
# Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
# 
# Combine1ExO <- Combine1ExO %>%
#   left_join(Rural, by = "LAD11CD")

@@

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
#  left_join(Rural, by = "LAD11CD") %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc),
         VacantsPerc = scale(VacantsPerc),
         price = scale(price),
         Extent = scale(Extent))

@@

test <- ModelStats %>% 
  select( X.Intercept., LUPdepExt, price, VacantsPerc) %>%
  gather

@@

Outcome <- bind_rows(data_frame(model = "Open Data", Accuracy = ModelStats2$Accuracy), 
data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )

Outcome %>%
  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3) +
  labs(title = "Density plot of the model outcomes, using custom FOI data vs generic open data")
SaveFig("CustomGenericOutcomes.pdf")

@@

#Plot the model coefficients

ModelStats2 %>%
  select(X.Intercept. ,Extent,price , VacantsPerc) %>%
  gather() %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 1000 random partitions")
SaveFig("ModelCoeffs.pdf")

#only one of these is necessary they hold almost the same information
ModelStats3 %>%
  select(X.Intercept. ,LUPdepExt,price , VacantsPerc) %>%
  gather() %>%
  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
  labs(title = "Coefficient values across 1000 random partitions")

@@

#Linear
set.seed(1983)
MultiCheckL <- 1:111 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

@@

      Comp.Type = case_when(
      .$Significant.Competition<0.5-tol ~"No",
      .$Significant.Competition>0.5 + tol ~"Yes",
      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
      )
  )

@@

#Plotting the expected range of

valuecheck <- sample(c(TRUE, FALSE), size = nrow(EnglandComp)*1000, replace = TRUE, prob = c(0.888, 1-0.888)) %>%
  matrix(., nrow=nrow(EnglandComp)) 
valuecheck <-   (valuecheck * ifelse(EnglandComp$Comp.Type == "Yes", TRUE, FALSE ) )%>% data.frame %>%
  bind_cols(select(EnglandComp, LAD11CD, Reference),.) %>%
  #Where ever the outcome is known it is reverted back to the true value, only estimated values are flipped.
  gather(key = "ID", value = "affected",-LAD11CD,-Reference) %>%
  mutate(Reference = as.logical(Reference)*1,
    affected = ifelse(is.na(Reference), affected, Reference)) %>%
  left_join(LadHomes) %>%
  group_by(ID, affected) %>%
  summarise(Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  group_by(affected) %>%
  mutate(Rank = percent_rank(Pop),
    Outlier = ifelse(percent_rank(Pop)<0.0275 | percent_rank(Pop)>0.975, "Yes", "No")) %>%
  group_by(ID) %>%
  mutate(affected = ifelse(affected == 1, "Yes", "No"),
         PercPop = Pop/sum(Pop))%>%
  ungroup #%>%
# mutate(PercPop = Pop)
#The NNUMBERS DONT MATCH WITH THE TABLE WHY?

#95 range is 78 to 84
affected <- valuecheck %>% filter(affected == "Yes")
q5 <- quantile(affected$PercPop,.05)
q95 <- quantile(affected$PercPop,.95)
x.dens <- density(affected$PercPop)
df.dens <- data.frame(x = x.dens$x, y = x.dens$y)
median(affected$PercPop)
affected %>%
  ggplot(aes(x = PercPop)) + geom_density() +
  geom_area(data = subset(df.dens, x <= q5), 
              aes(x=x,y=y))  +
    geom_area(data = subset(df.dens, x >= q95), 
              aes(x=x,y=y))+
labs(title = "The estimated percentage of English population affected by LUPs")
SaveFig("PopPercLUPAfftect.pdf")

valuecheck %>% filter(affected == "No") %>%
  ggplot(aes(x = PercPop)) + geom_density()

### 2017-09-05 allEnglandMap.Rmd
Cascading
Addede code to being trying to cascade. Included two new functions to smooth the code. the first identifies validnodes for the injection vector. the second balances the generation and demand of the valid nodes across islolated graph componants

  z <-m %>% addPolygons(
    fillColor = ~pal(Comp.Type),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")
    ) %>%
    addLegend(pal = pal, values = ~Comp.Type, opacity = 0.7, title = NULL,
              position = "bottomright")
```

>>>>

  z <-m %>% addPolygons(
    fillColor = ~pal(Comp.Type),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")
    ) %>%
    addLegend(pal = pal, values = ~Comp.Type, opacity = 0.7, title = NULL,
              position = "bottomright")

```{r}
  z

  mapshot(z, file = file.path(Figures, "EnglandMarket.pdf"))
```
